Import raw csv data, clean it, and generate new csv files

### 2023-02-03 outputs/paper/paper.qmd
General cleaning and adding comments
* Added a note to the incident data testing to describe an issue where the test returns two Booleans, one of which is false. Clarified this incident for the user.
* Fixed minor spacing issue with paper.qmd
Added more code comments

```{r}
#| messages: false
#| echo: false
#| warning: false
#### Preamble ####
# Title: The Response Time of Toronto's Paramedic Service: How effective is the city's emergency medical care?
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses
```

```{r}
#| messages: false
#| echo: false
#| warning: false
#| output: false
#### Workspace set-up ####
# Define required libraries 
library(lubridate)
library(tidyverse)
library(dplyr)
library(knitr)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)
```

```{r}
#| messages: false
#| echo: false
#| warning: false
#### Fetch and clean relevant data sets ####
# Fetch the the clean response data
clean_response_data <- readr::read_csv(here::here("inputs/data/clean_response_data.csv"), show_col_types = FALSE)

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Number of Emergency Medical Responses in Toronto (by year since 2014)"
#| label: fig-1
clean_performance_data |>
  # Define plot 
  ggplot(aes(
    x = year, 
    y = ems_responses
  )) +

@@

  # Render bar chart
  geom_bar(stat="identity", fill = "deepskyblue3")

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Emergency Medical Incidents and Dispatched Ambulances (in 2021)"
#| label: fig-2
summarized_incident_data <- clean_incident_data |>
  # Group data by incident type
  group_by(incident_type) |>

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Mandated Response Times for the Toronto Paramedic Services (as of 2021)"
#| label: fig-3
clean_response_data |>
  # Select type of response and estimated response plan 
  select(patient_category, plan_in_minutes) |>

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Percent of Calls Meeting Mandated Response Times (since 2013)"
#| label: fig-4
clean_response_data |>
  # Plot graphs, define x axis
  ggplot(aes(x=response_time_standard_year)) +

>>>>

```{r}
#| messages: false
#| echo: false
#| warning: false
#| output: false
#### Preamble ####
# Title: The Response Time of Toronto's Paramedic Service: How effective is the city's emergency medical care?
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses

#### Workspace set-up ####
# Define required libraries 
library(lubridate)
library(tidyverse)
library(dplyr)
library(knitr)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)

# Fetch the the clean response data
clean_response_data <- readr::read_csv(here::here("inputs/data/clean_response_data.csv"), show_col_types = FALSE)

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Number of Emergency Medical Responses in Toronto (by year since 2014)"
#| label: fig-1
#### Plot graph on the number of EMS responses in Toronto ####
clean_performance_data |>
  # Define plot 
  ggplot(aes(
    x = year, 
    y = ems_responses
  )) +

@@

  # Render bar chart
  geom_bar(stat="identity", fill = "deepskyblue3")
```

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Emergency Medical Incidents and Dispatched Ambulances (in 2021)"
#| label: fig-2
#### Create a table summarizing emergency medical incident data in Toronto ####
summarized_incident_data <- clean_incident_data |>
  # Group data by incident type
  group_by(incident_type) |>

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Mandated Response Times for the Toronto Paramedic Services (as of 2021)"
#| label: fig-3
#### Create a table outlining CTAS levels and response times ####
clean_response_data |>
  # Select type of response and estimated response plan 
  select(patient_category, plan_in_minutes) |>

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Percent of Calls Meeting Mandated Response Times (since 2013)"
#| label: fig-4
#### Create graphs plotting mandated and actual response times ####
clean_response_data |>
  # Plot graphs, define x axis
  ggplot(aes(x=response_time_standard_year)) +

### 2023-02-03 scripts/02-data_cleaning.qmd
Added more code comments

---
title: "Import raw csv data, clean it, and generate new csv files"
format: html
author: "Sebastian Rodriguez"
---
```{r}
#### Preamble ####
# Purpose: Import raw csv data, clean it, and generate new csv files
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses
```

```{r}
#### Workspace set-up ####
library(tidyverse)
library(dplyr)
library(here)
library(readr)
```

```{r}
# Fetch and clean the raw response data
clean_response_data <- readr::read_csv(here::here("inputs/data/raw_response_data.csv"), show_col_types = FALSE) |>
  # Change column naming format
  clean_names() |>

@@

```{r}
# Fetch and clean the raw performance data
clean_performance_data <- readr::read_csv(here::here("inputs/data/raw_performance_data.csv"), show_col_types = FALSE) |>
  # Change column naming format
  clean_names() |>

@@

```{r}
# Fetch and clean the raw incident data
clean_incident_data <- readr::read_csv(here::here("inputs/data/raw_incident_data.csv"), show_col_types = FALSE) |>
  # Change column naming format
  clean_names() |>

>>>>

---
title: "Import raw csv data, clean it, and generate new csv files"
format: html
author: "Sebastian Rodriguez"
---
```{r}
#### Preamble ####
# Purpose: Import raw csv data, clean it, and generate new csv files
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses

#### Workspace set-up ####
library(tidyverse)
library(dplyr)
library(here)
library(readr)
```

```{r}
#### Fetch and clean the raw response data ####
clean_response_data <- readr::read_csv(here::here("inputs/data/raw_response_data.csv"), show_col_types = FALSE) |>
  # Change column naming format
  clean_names() |>

@@

```{r}
 #### Fetch and clean the raw performance data  ####
clean_performance_data <- readr::read_csv(here::here("inputs/data/raw_performance_data.csv"), show_col_types = FALSE) |>
  # Change column naming format
  clean_names() |>

@@

```{r}
#### Fetch and clean the raw incident data ####
clean_incident_data <- readr::read_csv(here::here("inputs/data/raw_incident_data.csv"), show_col_types = FALSE) |>
  # Change column naming format
  clean_names() |>
